Corporate Security Solutions for BYOD:\\ A Novel User-Centric and Self-Adaptive System

### 2015-07-08 MUSES_vs_BYOD_solutions.tex
conflict?

On the other side, employees are able to access information and applications related to their personal lives, while staying connected to important work information when they need to perform. Finally, another known feature is also offered by Blackberry, so if the device gets lost or is stolen, or if the employee leaves the organization, there will be an option to wipe just work information which can be done remotely.

>>>>

On the other side, while KNOX allows to \textit{push} policies from the server to the devices, so they are available offline, Blackberry Balance only allows to read documents in this mode. Finally, another known feature is also offered by Blackberry, so if the device gets lost, it is stolen, or if the employee leaves the organization, there is an option to wipe just work information which can be done remotely.
